### 2018-04-04 Paper/sense.tex
...
..

\section{Derivative-based Sensitivity Analysis}
\label{sec:sense}

>>>>

\section{Sensitivity Analysis of the Inter-atomic Potential}
\label{sec:sense}

As discussed earlier in Section~\ref{sec:intro}, bulk thermal conductivity estimates in NEMD are dependent
on the choice of the inter-atomic potential as well as values associated with the individual potential parameters.
In the case of silicon, Stillinger-Weber is a commonly used potential and the proposed set of nominal values
have been used for a wide variety of systems. According Stillinger and Weber, the set of nominal values as provided
below in Table~\ref{tab:nom} is based on a constrained search in the 7D parameter space
to ensure structural stability and agreement with the available experimental data~\cite{Stillinger:1985}. However, it is
noteworthy that these estimates did not account for the presence of uncertainty due to experimental data, 
inadequacies pertaining to the potential function, and parametric uncertainties. Hence, it is critical
to understand the impact of such uncertainties on NEMD predictions for bulk thermal conductivity using
SW potential.
